## Load in necessary libraries

```{r, message=FALSE}
library(tidyverse)
library(purrr)
```

## Importing Democracy Data from Github

```{r, message=FALSE}
democracy_data <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2024/2024-11-05/democracy_data.csv')
```

## Describing the context of the data
This data has information on regimes of countries from 1950 to 2022. This includes what type of government the country has, who the ruler is, if they have fair and free elections, and tons of more information.

## Data Cleaning
There has been a fair amount of data cleaning done to the set. This includes renaming the variables, turning placeholder data (e.g. ?) into missing values, and splitting a month/year field into two separate variables.

# Part 4

## Summary on: Which countries have the highest proportion of postponed elections over time?

```{r}
# postponed_elections creates a variable prop_postponed that reports the
# proportion of years with postponed elections for each country
postponed_elections <- function(country, data = democracy_data){
  result <- data |>
    filter(country_name == country) |>
    arrange(year) |>
    mutate(
      postponed = has_postponed_election == TRUE
    ) |>
    summarise(prop_postponed = mean(postponed, na.rm = TRUE))
  
  return(result$prop_postponed)
}

postponed_data <- democracy_data |>
  distinct(country_name) |>
  mutate(prop_postponed = map_dbl(country_name, postponed_elections)) |>
  arrange(desc(prop_postponed))

ggplot(postponed_data[1:10, ], 
       aes(x = reorder(country_name, -prop_postponed), y = prop_postponed)) +
  geom_bar(stat = "identity", fill = "dodgerblue") +
  labs(
    title = "Countries with the Highest Proportion of Postponed Elections",
    x = "Country",
    y = "Proportion of Years with Postponed Elections"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
